---
title: "Online Food Delivery Service"
Author: "Members: Defensor - Echaveria - Quillo || Course-Yr-Sec: BSIT 2-C"
date: "2024-04-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Libraries
library("dplyr")
library("readr")
library("ggplot2")
```

```{r}
OFDSraw <- read_csv("database-RAW/Survey on Students' Perspectives of Online Food Delivery Service.csv")

OFDSraw <- slice(OFDSraw, -1)
#I sliced the first row of the data frame because is a test when I created the google form

top <- OFDSraw[13:23,]
top
```

Cleaning of age in data
```{r}
# Extract numeric values from 'age' column
OFDSage <- as.numeric(gsub("[^0-9.]", "", OFDSraw$Age))
tempOFDSraw <- OFDSraw

tempOFDSraw[["Age"]] <- OFDSage

OFDSraw <- tempOFDSraw

```


Plotting of age
```{r}
filtered_data <- tempOFDSraw[is.finite(OFDSraw$Age), ]

# Calculate range of finite ages
age_range <- range(filtered_data$Age)

# Create a histogram with more detailed x-axis
plotofage <- ggplot(data = filtered_data, aes(x = Age)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +  # Decrease binwidth for more detail
  scale_x_continuous(breaks = seq(floor(age_range[1]), ceiling(age_range[2]), by = 1)) +  # Custom breaks
  labs(title = "Distribution of Ages",
       x = "Age",
       y = "Frequency")

plotofagemean <- mean(filtered_data$Age)
plotofagemin <- min(filtered_data$Age)
plotofagemax <- max(filtered_data$Age)

#Min of Age
plotofagemin

#Mean of Age:
plotofagemean

#Max of Age
plotofagemax

```


Plotting the Frequency of Address
```{r}
address_freq <- table(tempOFDSraw$Address)

# Convert the frequency table to a data frame
address_df <- data.frame(Address = names(address_freq), Frequency = as.numeric(address_freq))

# Sort the data frame by frequency in descending order
address_df <- address_df[order(-address_df$Frequency), ]

# Plot the common addresses
ggplot(data = head(address_df, 10), aes(x = reorder(Address, Frequency), y = Frequency)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  # Flip the coordinates to display horizontally
  labs(title = "Top 10 Common Addresses",
       x = "Address",
       y = "Frequency")
```


Plotting the Frequency of Sex
```{r}
ggplot(data = OFDSraw, aes(x = Sex)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Distribution of Sex",
       x = "Sex",
       y = "Frequency")
```


Plotting the Frequency of Living Situation
```{r}
ggplot(data = OFDSraw, aes(x = OFDSraw$`Living Situation`)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Distribution of Living Situation",
       x = "Living Situation",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability
```


Plotting the Frequency of access to reliable transportation
```{r}
ggplot(data = OFDSraw, aes(x = OFDSraw$`Do you have access to reliable transportation(e.g., bike, carpool)?`)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Distribution of Access to Reliable Transportation",
       x = "Transportation Access",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability
```


Plotting the Frequency of Educational Background
```{r}
ggplot(data = OFDSraw, aes(x = OFDSraw$`Educational Background`)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Distribution of Educational Backgrounds",
       x = "Educational Background",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability
```


Plotting the Frequency for Average Weekly Income / allowance
```{r}
ggplot(data = OFDSraw, aes(x = OFDSraw$`Average Weekly Income / allowance`)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Distribution of Average Weekly Income/Allowance",
       x = "Income",
       y = "Frequency")
```


Plotting the Frequency for Frequency of Using Online Food Delivery Services
```{r}
ggplot(data = OFDSraw, aes(x = OFDSraw$`Frequency of Using Online Food Delivery Services`)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Frequency of Using Online Food Delivery Services",
       x = "Frequency",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability
```


Plotting the Frequency for Primary Reason for Using Online Food Delivery Services
```{r}
ggplot(data = OFDSraw, aes(x = OFDSraw$`Primary Reason for Using Online Food Delivery Services`)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Primary Reasons for Using Online Food Delivery Services",
       x = "Primary Reason",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability
```
